Beef Pricing Dynamics in the Canadian Grocery Market: A Comparative Analysis of Walmart and T&T

### 2024-11-28 paper/paper.qmd
charts caption revised

```{r}
#| label: fig-average_price_over_time
#| fig-cap: "Average Current Price Over Time"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-current_vs_old_price
#| fig-cap: "Heatmap of Price Levels between Current Price and Old Price of Beef"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: tbl-modelresults
#| tbl-cap: ""
#| echo: false
#| warning: false
#| message: false

>>>>

```{r}
#| label: fig-average_price_over_time
#| fig-cap: "Average Daily Current Price Over Time"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-current_vs_old_price
#| fig-cap: "Relationship Between Old and Current Beef Price Levels"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: tbl-modelresults
#| tbl-cap: "Beef model results"
#| echo: false
#| warning: false
#| message: false
